\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xcolor} %%furkhan
\usepackage{fancyhdr}
\usepackage[pdftex,
            colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref} 
\usepackage{array}
\usepackage{multirow}



%%\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%
%%above this
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
%%furkhan command
\newcommand{\resumeSubitemmodified}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \multirow{2}{*}
  {\textbf{\huge{Furkhan Shaikh}} 
  } & \textbf{Email :} \href{mailto:mohammadfurkhan@gmail.com}{mohammadfurkhan@gmail.com}\\ &
  \href{mailto:mohammedfurkhan.shaikh@mavs.uta.edu}{mohammedfurkhan.shaikh@mavs.uta.edu} \\
  
  \href{https://www.linkedin.com/in/furkhan-shaikh}{linkedin.com/in/furkhan-shaikh} \hspace{0.02cm}
  \href{https://www.github.com/FurkhanShaikh}{github.com/FurkhanShaikh}   & Arlington, Tx \textbf{Mobile :} +1-972-901-0479 \\
\end{tabular*}

% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \multirow{1}{*}
  
% \end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Texas at Arlington (UTA)}{Arlington, Texas}
      {Master of Science in Computer Science ; GPA: 4.0/4.0}{Aug. 2019 -- Dec 2021 (Expected)}
    \resumeSubheading
      {Shri Guru Gobind Singhji Institute of Engineering \& Technology (SGGSIE\&T)}{Nanded, India}
      {Bachelor of Technology -- Computer Science and Engineering; CGPA: 8.39/10}{Aug. 2014 -- June 2018}
     
  \resumeSubHeadingListEnd
  
\section{Fields of Interest}
    \resumeSubHeadingListStart
        \resumeItem
        {Artificial Intelligence, Machine Learning, Deep Learning, Natural Language Processing, Databases}{}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
%-----------INTERNSHIPS-----------------
% \section{Internships}
%   \resumeSubHeadingListStart
%     \resumeSubitemmodified{}
%     {}
%       \resumeItemListStart
%         \resumeItem{}
%           {}
%         \resumeItem{}
%           {}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd
   
%-----------PROJECTS-----------------
\section{Major Projects}
    \resumeSubHeadingListStart
    \resumeSubitemmodified{Alpaca Voice}
    {UTA (Oct 2019)}
   
      \resumeItemListStart
        \resumeItem{Implemented Alexa voice command for buying and selling shares of stock market}
          {}
        \resumeItem{Used Voiceflow's framework and Alpaca API to create the Alexa command and for testing}
          {}
        \resumeItem{Integrated with Google Spreadsheet to store and retrieve data for user in javascript}
          {}
        \resumeItem{\underline{2\textsuperscript{nd} Overall Winner, HackUTA}}
          {\href{https://devpost.com/software/alpaca-voice}{devpost.com/software/alpaca-voice}}
      \resumeItemListEnd
    \resumeSubitemmodified{Recurrent Neural Networks based Language Modelling}
    {SGGSIE\&T (Jan. 2018 - May 2018)}

      \resumeItemListStart
        \resumeItem{Implemented RNN for predicting words based on a sequence of past words in C}
          {}
        \resumeItem{Implementation works on huge vocabulary without resulting in large model size}
          {}
      \resumeItemListEnd
    \resumeSubitemmodified{Aqua Scorch Image Perceiver using Image Repositories}
    {SGGSIE\&T (Jan. 2018 - May 2018)}

      \resumeItemListStart
        \resumeItem{Detection of Water bodies and Burnt areas from given satellite image taken with AWiFS sensor}
          {}
        \resumeItem{Added support for multiprocessing and backend support for MongoDB in python.}
          {}
        \resumeItem{Created web-based frontend for image retreival and output using PHP, bootstrap.}
          {}
        \resumeItem{\underline{Best Student Project Award} 2018 by Tata Consultancy Services (TCS) (Nominated by the institute)}{}
        \resumeItem{Presented in Smart India Hackathon 2018 grand-finale under the problem statement of ISRO}
          {}
      \resumeItemListEnd
    \resumeSubitemmodified{Efficient Water Management for Greenland using Soil Moisture Sensor}
    { (Jan. 2016 - Mar. 2016)}

      \resumeItemListStart
        \resumeItem{Interfaced Raspberry Pi with Arduino Uno and Hygrometer sensor for auto-irrigation.}
            {}
        \resumeItem{Added support for data logging using Google REST API and MySQL database.}
            {}
        \resumeItem{Created web-based frontend for remote monitoring of system using PHP.}
            {}
        \resumeItem{\underline{2\textsuperscript{nd} prize}, My Green Idea 2017 BITS Pilani, Goa and was awarded an opportunity to work with Imagine Panaji, Government of Goa}
            {}
        \resumeItem{\underline{2\textsuperscript{nd} prize}, Design \& Development of Innovative Apps \& Appliances SGGSIE\&T 2016}
            {}
        \resumeItem{\underline{1\textsuperscript{st} Runner-ups}, APOGEE Innovation Challenge by Schneider Electric at BITS Pilani 2016}
            {}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------PUBLICATIONS-----------------
\section{Publications}
    \resumeSubHeadingListStart
        \resumeSubItem{Content Based Image Retrieval from AWiFS Images Repository of IRS Resourcesat-2 Satellite Based on Water Bodies and Burnt Areas \href{https://arxiv.org/abs/1809.10190}{(arXiv)}}{S. Kothawade, K. Mhaske, S. Sharma, \underline{Furkhan Shaikh}}
        \resumeSubItem{Efficient water management for greenland using soil moisture sensor, IEEE ICPEICES 2016. \href{https://doi.org/10.1109/ICPEICES.2016.7853281}{(IEEE-Xplore)}}{S.N. Kothawade, \underline{Shaikh Mohammed Furkhan}, K. S. Mhaske}
        
    \resumeSubHeadingListEnd

%-----------Programming Skills-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages :}{C (Advanced), Java (Intermediate), Python (Intermediate), SQL (Intermediate), PHP Laravel Framework (Intermediate), Javascript (Beginner)}
  \resumeSubHeadingListEnd
%-----------EXTRA-CURRICULARS-----------------
\section{Extra Curriculars}
    \resumeSubHeadingListStart
        \resumeSubItem{2\textsuperscript{nd} rank in school, All-India-Rank 4613, 10\textsuperscript{th} National Cyber Olympiad}{2010}
        \resumeSubItem{Coordinated \emph{Android App Development 2 days Workshop}}
        {at SGGSIET Oct 2016}
        \resumeSubItem{Member of \emph{Team-Sankalp}}
        {for organising campus activities at SGGSIET 2015-2016}
        \resumeItem{Workshops Attended:}{\emph{``Deep Learning using Cuda" by nvidia}; Machine Learning and High-Performance Computing by TCS; Internet-of-Things; Sensor Design and Implementation; Cyber-Security and Forensics}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
